---
title: "p8105_hw1_jg4891"
output: html_document
date: "2025-09-15"
---

```{r set up, include=FALSE}
library("moderndive")
library("tidyverse")
data(early_january_weather)

```

```{r description, include=FALSE}
names(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```

Early Janaurary weather dataset has following variables:origin, year, month, day, hour, temp,      dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. It has 358 rows and 15 columns. The mean temperature is 39.58212 fahrenheit degrees.

```{r scatterplot, echo = FALSE}
scatterplot <- ggplot(data = early_january_weather) +
  geom_point(mapping = aes(x = time_hour, y = temp, color = humid), size = 3)
print(scatterplot)
```
A scatterplot of humidity shows that it increases on average from below 40 to 100 as time passes by and temperature increases. 

```{r df,include=FALSE}
df = tibble(
  norm_samp = rnorm(10, mean = 1),
  norm_samp_pos = norm_samp > 0,
  vec_char = rep("First quiz", 10),         
  vec_factor = factor(rep(c("good", "bad", "average"), length.out = 10)) 
)
```


```{r mean,include=FALSE}
mean_norm_samp <- mean(pull(df, norm_samp))
mean_norm_samp_pos <- mean(pull(df, norm_samp_pos))
mean_vec_char <- mean(pull(df, vec_char))  
mean_vec_factor <- mean(pull(df, vec_factor)) 

```
The mean of the first variable is `r round(mean_norm_samp, digits = 2)`. 
The mean of the second variable is `r round(mean_norm_samp_pos, digits = 2)`.
The third and fourth variable doesn't have a mean because they are texts instead of numerical value or logical value.
